Handovers - SIPHER 7 Equivalent Income

### 2023-12-15 minos/validation/handovers_S7.Rmd

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'SIPHER7')
create.if.not.exists(save.path)

shall.we.save <- FALSE
```

# Weight Testing

```{r}
raw.weight <- raw.dat %>%
  select(pidp, time, weight) %>%
  group_by(time) %>%
  summarise(mean.weight = mean(weight, na.rm = TRUE))

ggplot(raw.weight, aes(x = time, y = mean.weight)) +
  geom_line()

raw.weight.WBI <- raw.dat %>%
  select(pidp, time, weight, ethnicity) %>%
  filter(ethnicity == 'WBI') %>%
  group_by(time) %>%
  summarise(mean.weight = mean(weight, na.rm=TRUE))

ggplot(raw.weight.WBI, aes(x=time, y = mean.weight)) +
  geom_line()

raw.weight.eth <- raw.dat %>%
  select(pidp, time, weight, ethnicity) %>%
  group_by(time, ethnicity) %>%
  summarise(mean.weight = mean(weight, na.rm = TRUE))

ggplot(raw.weight.eth, aes(x = time, y = mean.weight, group = ethnicity, color = ethnicity)) +
  geom_line()
```

@@

### Modified Lineplots

```{r}
handover_lineplots(raw.dat, base.dat, 'hh_income')
```

### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'hh_income')
```

@@

```{r}
# raw.inc <- raw.dat %>%
#   select(pidp, age, time, hh_income)
# base.inc <- base.dat %>%
#   select(pidp, age, time, hh_income)
# 
# income.spag <- rbind(raw.inc, base.inc)
# 
# spaghetti_plot(income.spag, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.inc, base.inc, income.spag)
```

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.ei <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(equivalent_income != -9) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2017]

raw.ei.2 <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  filter(equivalent_income != -9) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei.2 <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = ei.2, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income', subtitle = 'Wave 9 sample') +
  xlab('Year') +
  ylab('EI')

@@

### Modified Lineplots

```{r}
handover_lineplots(raw.dat, base.dat, 'equivalent_income')
```

### Check Replenishing Population

Might give us a clue about the big correction in first year of simulation?

```{r}
repl.file <- here::here('data', 'replenishing', 'replenishing_pop_2019-2070.csv')
repl.dat <- read.csv(repl.file)

repl.equiv <- repl.dat %>%
  select(time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

ggplot(repl.equiv, aes(x = time, y = equivalent_income)) +
  geom_line()
```

### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'equivalent_income')
```

@@

```{r}
# raw.ei <- raw.dat %>%
#   select(pidp, age, time, equivalent_income)
# base.ei <- base.dat %>%
#   select(pidp, age, time, equivalent_income)
# 
# ei.spag <- rbind(raw.ei, base.ei)
# 
# spaghetti_plot(base.ei, 'equivalent_income')
# 
# spaghetti_plot(ei.spag, 'equivalent_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.ei, base.ei, ei.spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

## just look at means in case the means are causing some problems
raw.dat.2 <- raw.dat
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
base.dat.2 <- base.dat
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3

handover_lineplots(raw.dat.2, base.dat.2, 'S7_neighbourhood_safety2')

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_labour_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_labour_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_labour_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

handover_lineplots(raw.dat, base.dat, 'S7_physical_health')

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_physical_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_physical_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_physical_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_mental_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_mental_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_mental_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

## loneliness only available from 2017 onwards
var <- filter(var, time >= 2017)

@@

pivoted <- filter(pivoted, time >= 2017)

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Job Sec

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')

tit <- 'Job NSSEC'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'job_sec.png',
         plot = last_plot(),
         path = save.path)
}

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat,
                                  df1.name = 'simulated', 
                                  df2 = raw.dat, 
                                  df2.name = 'raw', 
                                  var = 'job_sec')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'job_sec',
                 save = shall.we.save,
                 save.path = save.path)
```

>>>>

```{r}
start.year <- 2021
save.path <- here::here("plots", "handovers", 'SIPHER7')
create.if.not.exists(save.path)

shall.we.save <- TRUE
```

@@

@@

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

income.spag <- rbind(raw.inc, base.inc)

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

rm(raw.inc, base.inc, income.spag)
```

@@

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.ei <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.ei.2 <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei.2 <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = mean(equivalent_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

# Now plot
ggplot(data = ei.2, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income', subtitle = 'Wave 1 sample') +
  xlab('Year') +
  ylab('EI')

@@

@@

```{r}
raw.ei <- raw.dat %>%
  select(pidp, age, time, equivalent_income)
base.ei <- base.dat %>%
  select(pidp, age, time, equivalent_income)

ei.spag <- rbind(raw.ei, base.ei)

spaghetti_plot(base.ei, 'equivalent_income')

spaghetti_plot(ei.spag, 'equivalent_income',
               save = shall.we.save,
               save.path = save.path)

rm(raw.ei, base.ei, ei.spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, S7_housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_housing_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, S7_neighbourhood_safety)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_labour_state)
base.s <- base.dat %>%
  select(pidp, age, time, S7_labour_state)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_labour_state',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_physical_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_physical_health)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_physical_health',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_mental_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_mental_health)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'S7_mental_health',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

@@

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```
